### 2024-11-21 paper.tex
$ computation security

\usepackage{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{times}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{titling}
\usepackage{url}
\usepackage{xurl}

@@

Clearly, $L_0 = x_0\sqrt p$. We then express $L_1$ in terms of UniswapV3
trading curve (equation (2.1) of the paper \cite{uniswapv3}) by taking
liqudity on the right, and $k$ as the base range \texttt{PriceFactor}:
\[
L_1 = x_1\frac{\sqrt{p}\sqrt{pk}}{\sqrt{pk}-\sqrt{p}}
    = x_1\frac{\sqrt{pk}}{\sqrt k - 1}
\]
Substituting then into our $w$ invariant:
\begin{equation*}
\begin{split}
w &= \frac{L_0}{L_0 + L_1}\\
  &= \frac{x_0\sqrt p}{x_0\sqrt p + \frac{x_1\sqrt{pk}}{\sqrt k - 1}}\\
  &= x_0\left({x_0 + \frac{x_1\sqrt{k}}{\sqrt k - 1}}\right)^{-1}\\
  &= x_0\left(
    \frac{x_0(\sqrt k - 1) + x_1\sqrt k}{\sqrt k - 1}
  \right)^{-1}\\
  &= \frac{x_0(\sqrt k -1)}{x_0(\sqrt k -1) + (x-x_0)\sqrt k}\\
  &= \frac{x_0\sqrt k - x_0}{x_0\sqrt k -x_0 + x\sqrt k - x_0\sqrt k}\\
  &= \frac{x_0\sqrt k - x_0}{x\sqrt k - x_0} =w
  \stackrel{(A)}\implies x_0 = \frac{\sqrt k wx}{\sqrt k + w - 1}
\end{split}
\end{equation*}
Where at step $(A)$ we simply solve for $x_0$. And once we know $x_0$,
we of course can simply get $y_0$ as $y_0 = x_0p$, which ensures the
reserves to be in proportion. We can ensure this derivation is sound
in multiple ways. For example, by proving $x_0 \leq x \leq X$ (left as an exercise).
Intuition also tells us the final expression for calculating $x_0$ makes sense.
Why would we care about $Y$, $y$ or $p$ to compute the allocation of tokens $X$
needed if price factors already ensure liquidity stays constant for any position
centered at the current price? Its also expected that, by symmetry, a dual expression
for calculating $y_0$ as function of $k$, $w$ and $y$ exists, but that would 
introduce extra computational overhead, as we can simply compute one reserve from
the other using the current price $p$.

\subsection{Computation security proof}
Work in progress. I already got the proof in a obsidian note, just need
to review and formalize it.

>>>>

\usepackage{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{times}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{titling}
\usepackage{url}
\usepackage{xurl}
\usepackage{minted}
\usepackage{enumitem}

@@

Clearly, $L_0 = x_0\sqrt p$. We then express $L_1$ in terms of UniswapV3
trading curve (equation (2.1) of the paper \cite{uniswapv3}) by taking
liqudity on the right, and $k$ as the base range \texttt{PriceFactor}:
\[
L_1 = x_1\frac{\sqrt{p}\sqrt{pk}}{\sqrt{pk}-\sqrt{p}}
    = x_1\frac{\sqrt{pk}}{\sqrt k - 1}
\]
Substituting then into our $w$ invariant:
\begin{equation*}
\begin{split}
w &= \frac{L_0}{L_0 + L_1}\\
  &= \frac{x_0\sqrt p}{x_0\sqrt p + \frac{x_1\sqrt{pk}}{\sqrt k - 1}}\\
  &= x_0\left({x_0 + \frac{x_1\sqrt{k}}{\sqrt k - 1}}\right)^{-1}\\
  &= x_0\left(
    \frac{x_0(\sqrt k - 1) + x_1\sqrt k}{\sqrt k - 1}
  \right)^{-1}\\
  &= \frac{x_0(\sqrt k -1)}{x_0(\sqrt k -1) + (x-x_0)\sqrt k}\\
  &= \frac{x_0\sqrt k - x_0}{x_0\sqrt k -x_0 + x\sqrt k - x_0\sqrt k}\\
  &= \frac{x_0\sqrt k - x_0}{x\sqrt k - x_0} =w
  \stackrel{(A)}\implies x_0 = \frac{\sqrt k wx}{\sqrt k + w - 1}
\end{split}
\end{equation*}
Where at step $(A)$ we simply solve for $x_0$. And once we know $x_0$,
we of course can simply get $y_0$ as $y_0 = x_0p$, which ensures the
reserves to be in proportion. We can ensure this derivation is sound
in multiple ways. For example, by proving $x_0 \leq x \leq X$ (left as an exercise).
Intuition also tells us the final expression for calculating $x_0$ makes sense.
Why would we care about $Y$, $y$ or $p$ to compute the allocation of tokens $x_0$,
if $y_0$ is already its dual, as the position is balanced?

\break
\subsection{Computation security proof}
We now prove that the way $x_0$ is computed in the \texttt{magma-vaults} codebase
is secure. Thus considered the implementation:
\begin{minted}[fontsize=\small]{rust}
pub fn calc_x0(k: &PriceFactor, w: &Weight, x: Decimal) -> Decimal {
    if w.is_zero() { return Decimal::zero() }
    do_me! {
        let sqrt_k = k.0.sqrt();

        let numerator = w.mul_dec(&sqrt_k);

        let numerator = Decimal256::from(numerator)
            .checked_mul(x.into())?;                         // (1)

        let denominator = sqrt_k
            .checked_sub(Decimal::one())?                    // (2)
            .checked_add(w.0)?;                              // (3)

        let x0 = numerator.checked_div(denominator.into())?; // (4)
        Decimal::try_from(x0)?                               // (5)
    }.unwrap()
}
\end{minted}
The \texttt{do\_me!} macro only creates a \texttt{anyhow::Error} closure
and runs it, so we only need to ensure the commented lines wont produce
any errors:
\begin{enumerate}[label=(\arabic*).]
    \item Wont overflow as $(2^{128} - 1)^2 < 2^{256} - 1$.
    \item Wont underflow as $k\in[1, \infty)$, thus $\sqrt k - 1 = 0$ in the
        worst case.
    \item Wont overflow as $w\in[0, 1]$, and we just subtracted 1 from $\sqrt
        k$ .
    \item Could only produce a division by zero if $\sqrt k -  1 + w = 0$.
        Assume $k= 1$, then $\sqrt k - 1 + w = 0 \iff w = 0$, in which case
        $x_0$ computation is trivial (see first line of the implementation).
        Note that also $k = 1 \land w = 0$ produces a vault with generally idle
        capital and only limit positions (which the first version does not
        support). On the other hand, the division wont overflow because $x_0
        \leq x$, as stated earlier.
    \item Finally, the downgrade to 128 bits wont fail because, again, $x_0
        \leq x$, but $x$ fits in 128 bits by definition.
\end{enumerate}
